ext_risk_copula

### 2019-02-16 ext_risk_copula.Rmd
upto msmith fixed

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
seed<-101
source("mtime.R")
source("mydispersal.R")
```

#Ricker model :
```{r sim_ricker, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
library(abind)
rlist<-c(0,0.1,0.3,0.5,0.7,0.9,1.0,1.1,1.3,1.5,1.7,1.9) #rc = 1
numsims<-10000
numsteps<-25
numlocs<-5
K<-50
scl<-1
ext_thrs<-K/10
model<-"ricker"

@@

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right,s$noise_avg_acf_left,s$noise_avg_acf_right)
    res_ricker_local<-abind(res_ricker_local,temp_mat,along = 3)

@@

anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right","noise_avg_acf_left","noise_avg_acf_right")
dimnames(res_ricker_local)<-list(NULL,cnm,anm)

@@

# For global dispersion
res_ricker_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,K)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc)

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right,s$noise_avg_acf_left,s$noise_avg_acf_right)
    res_ricker_global<-abind(res_ricker_global,temp_mat,along = 3)
}
anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right","noise_avg_acf_left","noise_avg_acf_right")
dimnames(res_ricker_global)<-list(NULL,cnm,anm)
saveRDS(res_ricker_global,paste(resloc,"res_ricker_global.RDS",sep=""))
```

@@

  lines(s$d, s$noise_avg_acf_left, col="green")

@@

```{r sim_hassell, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)

@@

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right,s$noise_avg_acf_left,s$noise_avg_acf_right)
    res_hassell_local<-abind(res_hassell_local,temp_mat,along = 3)

@@

anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right","noise_avg_acf_left","noise_avg_acf_right")
dimnames(res_hassell_local)<-list(NULL,cnm,anm)

@@

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right,s$noise_avg_acf_left,s$noise_avg_acf_right)
    res_hassell_global<-abind(res_hassell_global,temp_mat,along = 3)
}
anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right","noise_avg_acf_left","noise_avg_acf_right")
dimnames(res_hassell_global)<-list(NULL,cnm,anm)
saveRDS(res_hassell_global,paste(resloc,"res_hassell_global.RDS",sep=""))
```

@@

```{r fig_msmith_scl_0.8, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)

@@

rc<-b/(b-1)
rlist<-sort(c(seq(from=1.2,to=2.8,by=0.2),rc))

@@

# plot for local dispersal in D matrix 
pdf(paste(resloc,"msmith_ext_risk_local_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.2))
for(i in c(1:length(rlist))){
    r<-rlist[i]
    params<-c(r,a,b)
    K_e<-((r-1)^(1/b))/a
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,ploton = F)
    msmith_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    msmith_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

saveRDS(msmith_extrisk_d0,paste(resloc,"msmith_extrisk_d0.RDS",sep=""))

# plot for global dispersal in D matrix 
pdf(paste(resloc,"msmith_ext_risk_global_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.2))
for(r in rlist){
    params<-c(r,a,b)
    K_e<-((r-1)^(1/b))/a
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

# Plot ext_risk_d0
msmith_extrisk_d0$CI0.025left<-qbinom(p=0.025,size=numsims,prob=msmith_extrisk_d0$risk_left_d0)/numsims
msmith_extrisk_d0$CI0.975left<-qbinom(p=0.975,size=numsims,prob=msmith_extrisk_d0$risk_left_d0)/numsims

@@

pdf(paste(resloc,"msmith_extrisk_d0.pdf",sep=""),height=6,width=6)
plot(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = c(1.2,2.8),xlab="r",ylab="ext_risk",cex.lab=1.5,pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025left,x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
seed<-101
library(abind)
source("mtime.R")
```

#Ricker model :
```{r sim_ricker, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")
rlist<-c(0,0.1,0.3,0.5,0.7,0.9,1.0,1.1,1.3,1.5,1.7,1.9) #rc = 1
numsims<-10000
numsteps<-25
numlocs<-5
K<-50
scl<-1
ext_thrs<-K/10
model<-"ricker"

@@

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right)
    res_ricker_local<-abind(res_ricker_local,temp_mat,along = 3)

@@

anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_ricker_local)<-list(NULL,cnm,anm)

@@

# For global dispersion
res_ricker_global<-c()

for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,K)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc)

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right)
    res_ricker_global<-abind(res_ricker_global,temp_mat,along = 3)
}

anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_ricker_global)<-list(NULL,cnm,anm)
saveRDS(res_ricker_global,paste(resloc,"res_ricker_global.RDS",sep=""))
```

@@

@@

```{r sim_hassell, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

@@

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right)
    res_hassell_local<-abind(res_hassell_local,temp_mat,along = 3)

@@

anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_hassell_local)<-list(NULL,cnm,anm)

@@

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right)
    res_hassell_global<-abind(res_hassell_global,temp_mat,along = 3)
}
anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_hassell_global)<-list(NULL,cnm,anm)
saveRDS(res_hassell_global,paste(resloc,"res_hassell_global.RDS",sep=""))
```

@@

```{r sim_msmith, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

@@

rc_msmith<-b/(b-1)
rlist<-sort(c(seq(from=1.2,to=2.8,by=0.2),rc_msmith))

@@

#for local dispersal in D matrix 
res_msmith_local<-c()

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,a,b)
    K_e<-((r-1)^(1/b))/a
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc)

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right)
    res_msmith_local<-abind(res_msmith_local,temp_mat,along = 3)

    msmith_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    msmith_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
}

anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_msmith_local)<-list(NULL,cnm,anm)

saveRDS(msmith_extrisk_d0,paste(resloc,"msmith_extrisk_d0.RDS",sep=""))
saveRDS(res_msmith_local,paste(resloc,"res_msmith_local.RDS",sep=""))

# For global dispersal in D matrix 
res_msmith_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,a,b)
    K_e<-((r-1)^(1/b))/a
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc)

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right)
    res_msmith_global<-abind(res_msmith_global,temp_mat,along = 3)
}
anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_msmith_global)<-list(NULL,cnm,anm)
saveRDS(res_msmith_global,paste(resloc,"res_msmith_global.RDS",sep=""))
```

```{r fig_msmith, echo=F, results="hide",cache=T, cache.extra=list(seed,res_msmith_local,res_msmith_global)}
pdf(paste(resloc,"msmith_ext_risk_local_disp.pdf",sep=""),height=9,width=15)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,6.2))

for(i in 1:dim(res_msmith_local)[3]){
  s<-res_msmith_local[,,i]
  s<-as.data.frame(s)

for(i in 1:dim(res_msmith_global)[3]){
  s<-res_msmith_global[,,i]
  s<-as.data.frame(s)

```{r fig_msmith_extrisk_d0, echo=F,results="hide"}
set.seed(seed)

msmith_extrisk_d0<-readRDS(paste(resloc,"msmith_extrisk_d0.RDS",sep=""))
numsims<-10000
msmith_extrisk_d0$CI0.025left<-qbinom(p=0.025,size=numsims,prob=msmith_extrisk_d0$risk_left_d0)/numsims
msmith_extrisk_d0$CI0.975left<-qbinom(p=0.975,size=numsims,prob=msmith_extrisk_d0$risk_left_d0)/numsims

@@

pdf(paste(resloc,"msmith_extrisk_d0.pdf",sep=""),height=6,width=6)
plot(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = c(1.2,2.8),xlab="r",ylab="ext_risk",cex.lab=1.5,pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025left,x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_msmith,lty="dotted")
